---
title: "Find Sites"
author: "David Carslaw"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
vignette: >
  %\VignetteIndexEntry{Find Sites}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Show all sites

The function to use to find which sites are available is `getMeta`. While this function can be run using different options, it can be easiest to run it without any options. This produces a map of all the available sites, which can be quickly accessed.

Click to expand the markers until you find the site of interest (shown by a blue marker). This reveals some site information including the site name and the start and end date of available data. The most important information revealed in the marker is the **code**, which is used to access the data.

```{r eval=FALSE}
library(worldmet)

getMeta()
```


```{r fig.width=10,fig.height=7,echo=FALSE}
library(worldmet)

getMeta(returnMap = TRUE)
```

When using `getMeta` it will probably be useful to read the information into a data frame e.g. `met_info <- getMeta()`.

# Search based on latitude and longitude

Often, one has an idea of the region in which a site is of interest. For example, if the interest was in sites close to London, the latitude and longitude can be supplied and a search is carried out of the 10 nearest sites to that location. There is also an option `n` that can be used in change the number of nearest sites shown. If a lat/lon is provided, clicking on the blue marker will show the approximate distance between the site and the search coordinates.

```{r eval=FALSE}
getMeta(lat = 51.5, lon = 0)
```


```{r fig.width=10,fig.height=7,echo=FALSE}
library(worldmet)

getMeta(lat = 51.5, lon = 0, returnMap = TRUE)
```
